Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2021-04-23 docs/00-manuscripts/ieee/ieee-manuscript.tex
wording

The PCA-based correlation analysis showed that, depending on the feature set, between two (HR) and 42 (NRI) \ac{PC} are needed to explain 95\% of variance.
The less PCs are needed to reach a high proportion of variance explained the more similar the individual features are to each other.
Hence, a high intra-feature correlation can be observed for feature set HR which reaches 96\% with only two PCs.
Feature sets NRI and VI are more diverse and require 42 (NRI) and 12 (VI) PCs to explain 95\% of the variance in the data, respectively.

>>>>

The PCA-based correlation analysis showed that, depending on the feature set, between two (HR) and 42 (NRI) \ac{PC} are needed to explain 95\% of variance.
The fewer PCs are needed to reach a high proportion of variance explained the more similar the individual features are to each other.
Hence, a high correlation can be observed for feature set HR which reaches 96\% with only two PCs.
Feature sets NRI and VI are more diverse and require 42 (NRI) and 12 (VI) PCs to explain 95\% of the variance in the data, respectively.
